---
title: "International Year - Pledge Maker Progress"
author: "Fabio Thoma"
date: "`r Sys.Date()`"
output:
  bookdown::gitbook:
    split_by: none
documentclass: book
biblio-style: apalike
link-citations: yes
site: bookdown::bookdown_site
---


```{r,warning = FALSE, message = FALSE, echo=FALSE}
#rm(list = ls())

library(tidyverse)
library(googledrive)
library(readxl)
library(plotly)
library(dplyr)
library(htmlwidgets)

library(tidyr)
library(stringr)

```


```{r,warning = FALSE, message = FALSE, echo=FALSE}
setwd("/Users/fabiothoma/Desktop/awesome-book_2/v22_12")


ENG <- read_excel("Pledge Makers Progress - IY - EN (Responses).xlsx")

FRA <- read_excel("Pledge Makers Progress - IY - FR (Responses).xlsx")

ESP <- read_excel("Pledge Makers Progress - IY - ESP (Responses).xlsx")

number_resp <- nrow(ENG) + nrow(FRA) + nrow(ESP) - 1

share_resp <- round((number_resp/306 * 100),2)

```



# Overview of survey


This brief report provides an overview of the progress survey on the International Year pledges. In total, more than 352 pledges were submitted by a variety of pledgemakers. All pledges went through a peer review process and 306 pledges were published on the [endchildlabour.org](endchildlabour.org) website. 

The International Year team launched the survey on 26 November. To date (`r Sys.Date()`), `r number_resp` surveys were submitted corresponding to `r share_resp` % of all pledgemakers. 
  

# Progress made in 2021

```{r,warning = FALSE, message = FALSE, echo=FALSE}

# Which answer best describes the progress made on your 2021 Action Pledge so far?

# Delete one entry 
ENG <- ENG[-c(27),]

names(ENG)[4] <- "Progress"

names(FRA)[4] <- "Progress"

names(ESP)[4] <- "Progress"


# French - change names

#replace_French_Progress <- function(x,y){
#  str_replace_all(FRA$Progress, y, z)
#}

#replace_French("Progress","Déjà réalisée","Already completed")

FRA$Progress <- str_replace_all(FRA$Progress, "Déjà réalisée", "Already completed")

FRA$Progress <-  str_replace_all(FRA$Progress, "Autre", "Other")

FRA$Progress <- str_replace_all(FRA$Progress, "Des progrès ont été réalisés, mais ils prendront plus de temps qu'en 2021","Progress has been made, but it will take longer than 2021")

FRA$Progress <- str_replace_all(FRA$Progress, "En bonne voie d’être réalisée d'ici la fin de 2021","On track to complete it by the end of 2021")

FRA$Progress <-  str_replace_all(FRA$Progress, "Pas encore de progrès", "No progress yet")




# Spanish - change names


ESP$Progress <- str_replace_all(ESP$Progress, "Ya completado", "Already completed")

ESP$Progress <-  str_replace_all(ESP$Progress, "Otra respuesta", "Other")

ESP$Progress <- str_replace_all(ESP$Progress, "Se han hecho progresos, pero se completará después de 2021","Progress has been made, but it will take longer than 2021")

ESP$Progress <- str_replace_all(ESP$Progress, "En vías de completarse a finales de 2021","On track to complete it by the end of 2021")

#ESP$Progress <-  str_replace_all(ESP$Progress, "Otra respuesta", "No progress yet")



# Can maybe be made easier

eng_progress <- data.frame(ENG$Progress) 
names(eng_progress) <- "Progress"

fra_progress <- data.frame(FRA$Progress) 
names(fra_progress) <- "Progress"

esp_progress <- data.frame(ESP$Progress)
names(esp_progress) <- "Progress"

progress <- rbind(eng_progress,fra_progress,esp_progress)


progress <- progress %>%
  count(Progress) 

#%>%
#  mutate(pct = n / sum(n),
#         pctlabel = paste0(round(pct*100), "%"))


fig <- plot_ly(progress, labels = ~Progress, values = ~n, type = 'pie')

# Using the international year colours
colors <- c('#8D094A', '#CA0148', '#146C77', '#F6B940', '#052538')


fig <- fig %>% layout(title = 'Progress on pledge implmentation',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

#fig


fig2 <- plot_ly(progress, labels = ~Progress, values = ~n, type = 'pie',
                              marker = list(colors = colors,
                      line = list(color = '#FFFFFF', width = 1)))


fig2 <- fig2 %>% layout(title = 'Progress made 2021 Action Pledge',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

fig2


saveWidget(fig2, "fig.html")
temp_file_proc <- tempfile(pattern = "", fileext = ".png")

#webshot("fig.html", temp_file_proc)




```

<h3>Other progress made in 2021</h3>

```{r,warning = FALSE, message = FALSE, echo=FALSE}


names(ENG)[5] <- "Progress_other"

names(FRA)[5] <- "Progress_other"

names(ESP)[5] <- "Progress_other"




progress_other_eng <- ENG %>% select(5)
progress_other_fra <- FRA %>% select(5)
progress_other_esp <- ESP %>% select(5)




progress_other <- rbind(progress_other_eng,progress_other_fra,progress_other_esp)


progress_other_eng_org <- ENG %>% select(27)
names(progress_other_eng_org)[1] <- "progress_other_eng_org"
progress_other_fra_org <- FRA %>% select(27)
names(progress_other_fra_org)[1] <- "progress_other_eng_org"
progress_other_esp_org <- ESP %>% select(27)
names(progress_other_esp_org)[1] <- "progress_other_eng_org"

progress_other_org <- rbind(progress_other_eng_org,progress_other_fra_org,progress_other_esp_org)

progress_other_df <- data.frame(progress_other,progress_other_org )

names(progress_other_df)[1] <- "Original"

names(progress_other_df)[2] <- "English translations"

progress_other_df <- progress_other_df[complete.cases(progress_other_df[ , 1]),]

library(DT)

DT::datatable(progress_other_df,caption= "What other progress did materialize in 2021?")

```
```{r,warning = FALSE, message = FALSE, echo=FALSE}


# Make a formula for the table 

other_table <- function(x,y){

names(ENG)[x] <- "Other"

names(FRA)[x] <- "Other"

names(ESP)[x] <- "Other"




Other_eng <- ENG %>% select(x)
Other_fra <- FRA %>% select(x)
Other_esp <- ESP %>% select(x)




Other_org_df <- rbind(Other_eng,Other_fra,Other_esp)


Other_eng_trans <- ENG %>% select(y)
names(Other_eng_trans)[1] <- "other_eng_trans"
Other_fr_trans <- FRA %>% select(y)
names(Other_fr_trans)[1] <- "other_eng_trans"
Other_es_trans <- ESP %>% select(y)
names(Other_es_trans)[1] <- "other_eng_trans"

other_trans <- rbind(Other_eng_trans,Other_fr_trans,Other_es_trans)

other_df <- data.frame(Other_org_df,other_trans )

names(other_df)[1] <- "Original"

names(other_df)[2] <- "English translations"

other_df <- other_df[complete.cases(other_df[ , 1]),]

  
}

#progress_other_df1 <- other_table(5,27)


library(DT)

#DT::datatable(progress_other_df1,caption= "What other progress did materialize in 2021?")

```



# Accelerate action

```{r,warning = FALSE, message = FALSE, echo=FALSE}

# In your opinion, did the pledge process help you accelerate action to end child labour?


names(ENG)[7] <- "Accelerate"
names(FRA)[7] <- "Accelerate"
names(ESP)[7] <- "Accelerate"



# Change French 


replace_French_Accelerate <- function(x,y){
  str_replace_all(FRA$Accelerate, x, y)
}




FRA$Accelerate <- replace_French_Accelerate("Il a permis de mobiliser des soutiens internes","It helped to mobilise internal support")

FRA$Accelerate <- replace_French_Accelerate("Nous avons pu maximiser l'impact en une seule année","It helped us maximise impact in a single year")

FRA$Accelerate <- replace_French_Accelerate("Nous avons pu acquérir et utiliser dans nos activités des connaissances sur le travail des enfants","It helped to gain knowledge on child labour, which was used in our activities")

FRA$Accelerate <- replace_French_Accelerate("Nous avons pu faire le point et réévaluer","It allowed us to take stock and reassess")


FRA$Accelerate <- replace_French_Accelerate("Non, le processus d'engagement n'a pas aidé à accélérer les progrès pour mettre fin au travail des enfants","No, the pledge process did not help to accelerate progress to end child labour")


# Spanish




replace_Spanish_Accelerate <- function(x,y){
  str_replace_all(ESP$Accelerate, x, y)
}




ESP$Accelerate <- replace_Spanish_Accelerate("Nos ha ayudado a movilizar apoyo interno","It helped to mobilise internal support")

ESP$Accelerate <- replace_Spanish_Accelerate("Nos ha ayudado a maximizar el impacto en un solo año","It helped us maximise impact in a single year")

ESP$Accelerate <- replace_Spanish_Accelerate("Nos ha ayudado a adquirir conocimientos sobre el trabajo infantil que hemos utilizado en nuestras actividades","It helped to gain knowledge on child labour, which was used in our activities")

ESP$Accelerate <- replace_Spanish_Accelerate("Nos ha permitido hacer balance y reevaluar la situación","It allowed us to take stock and reassess")

ESP$Accelerate <-  str_replace_all(ESP$Accelerate, "Otra respuesta", "Other")


#ESP$Accelerate <- replace_Spanish_Accelerate("Non, le processus d'engagement n'a pas aidé à accélérer les progrès pour mettre fin au travail des enfants","No, the engagement process has not helped accelerate progress to end child labor")



# Convert to ind. dataframes and bind together



eng_accelerate <- data.frame(ENG$Accelerate) 
names(eng_accelerate) <- "Accelerate"

fra_accelerate <- data.frame(FRA$Accelerate) 
names(fra_accelerate) <- "Accelerate"

esp_accelerate <- data.frame(ESP$Accelerate)
names(esp_accelerate) <- "Accelerate"


accelerate <- rbind(eng_accelerate,fra_accelerate,esp_accelerate)


accelerate <- accelerate %>% select(1) %>%
    mutate(Accelerate = strsplit(as.character(Accelerate), ", I")) %>% 
    unnest(Accelerate)


accelerate$Accelerate <- ifelse(startsWith(accelerate$Accelerate, 't '), str_replace_all(accelerate$Accelerate,"t ","It "),accelerate$Accelerate)



accelerate <- accelerate %>% select(1) %>% mutate(Accelerate = strsplit(as.character(Accelerate), ", O")) %>% unnest(Accelerate)

accelerate$Accelerate <- ifelse(startsWith(accelerate$Accelerate, 'ther'), str_replace_all(accelerate$Accelerate,"ther","Other"),accelerate$Accelerate)



accelerate$Accelerate <- str_replace_all(accelerate$Accelerate,"impacIt","impact")

accelerate_action <- accelerate %>%
  count(Accelerate) 

# Ordering dataframe


accelerate_action$Accelerate <- factor(accelerate_action$Accelerate, levels = unique(accelerate_action$Accelerate)[order(accelerate_action$n, decreasing = TRUE)])


colors2 <- c('#8D094A', '#CA0148', '#146C77', '#F6B940', '#052538','#A5A5A5','#FC9C08','#CA0148')


#fig_accelerate1 <- plot_ly(accelerate_action, y = ~Accelerate, x = ~n, type = 'bar',orientation='h')

#fig_accelerate1

fig_accelerate <- plot_ly(accelerate_action, y = ~n, x = ~Accelerate, color= ~Accelerate, type = 'bar',
              marker = list(colors = colors2,
                   line = list(color = '#FFFFFF', width = 1)))


fig_accelerate <- fig_accelerate %>% layout(title = 'Did the pledge process help you <br> accelerate action to end child labour? (Multiple Choice)',showlegend = FALSE,margin = list(b = 160), xaxis = list(tickfont = list(size = 10)))
fig_accelerate



#p <- ggplot(data=accelerate_action, aes(x=Accelerate, y=n)) +
#    geom_bar(stat="identity", position=position_dodge(), colour="black") +
#    scale_fill_manual(values=c('#8D094A', '#CA0148', '#146C77', '#F6B940', #'#052538','#A5A5A5','#FC9C08','#CA0148'))


#fig <- ggplotly(p)


#accelerate_action %>% order(accelerate_action$n,decreasing=TRUE)

#accelerate <- accelerate %>% layout(title = 'How did the pledge help accelerate action',
#         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
#         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))



```


<h3>Accelerate action - Other </h3>

```{r,warning = FALSE, message = FALSE, echo=FALSE}

accelerate_other_df1 <- other_table(8,28)


DT::datatable(accelerate_other_df1,caption= "Other Accelerate Action")

```

  
# Learning from pledgemaker community 

```{r,warning = FALSE, message = FALSE, echo=FALSE}

# Have you learnt from the pledgemaker community?

names(ENG)[9] <- "Learning"

names(FRA)[9] <- "Learning"

names(ESP)[9] <- "Learning"


# Change French into English


replace_French_Learning<- function(x,y){
  str_replace_all(FRA$Learning, x, y)
}




FRA$Learning <- replace_French_Learning("Nous avons obtenu des conseils d'autres contributeurs","We gained tips from other pledgemakers")

FRA$Learning <- replace_French_Learning("Nous avons été inspirés par d'autres contributeurs","We were inspired by other pledgemakers")

FRA$Learning <- replace_French_Learning("Nous avons contacté d'autres contributeurs et /ou avons collaboré avec eux","We reached out to and/or collaborated with other pledgemakers")

FRA$Learning <- replace_French_Learning("Non, nous n'avons pas appris de la communauté des donateurs","No, we have not learnt from the pledgemaker community")



# Change Spanish into English


replace_Spanish_Learning<- function(x,y){
  str_replace_all(ESP$Learning, x, y)
}



ESP$Learning <- replace_Spanish_Learning("Hemos obtenido consejos de otras personas que han hecho compromisos","We gained tips from other pledgemakers")

ESP$Learning <- replace_Spanish_Learning("Nos hemos inspirado en otras personas que han hecho compromisos","We were inspired by other pledgemakers")

ESP$Learning <- replace_Spanish_Learning("Nos hemos puesto en contacto y/o hemos colaborado con otras personas que han hecho compromisos","We reached out to and/or collaborated with other pledgemakers")

ESP$Learning <- replace_Spanish_Learning("Otra respuesta","Other")






# Convert to ind. dataframes and bind together



eng_learning <- data.frame(ENG$Learning) 
names(eng_learning) <- "Learning"

fra_learning <- data.frame(FRA$Learning) 
names(fra_learning) <- "Learning"

esp_learning <- data.frame(ESP$Learning)
names(esp_learning) <- "Learning"


learning <- rbind(eng_learning,fra_learning,esp_learning)

learning2 <- rbind(eng_learning,fra_learning,esp_learning)


# Splitting cells



learning <- learning %>% 
    mutate(Learning = strsplit(as.character(Learning), ", W")) %>% 
    unnest(Learning)


learning$Learning <- ifelse(startsWith(learning$Learning, 'e '), str_replace_all(learning$Learning,"e ","We "),learning$Learning)


learning <- learning %>%
  count(Learning) 

learning_plot <- plot_ly(learning, labels = ~Learning, values = ~n, type = 'pie',
                              marker = list(colors = colors,
                      line = list(color = '#FFFFFF', width = 1)))


learning_plot <- learning_plot %>% layout(title = 'Have you learnt <br> from the pledgemaker community? (Multiple Choice)',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

learning_plot


```


<h3> Learning from pledgemaker community - Other </h3>


```{r,warning = FALSE, message = FALSE, echo=FALSE}

learning_other_df1 <- other_table(10,29)

DT::datatable(learning_other_df1,caption= "Learning from pledgemaker community - Other ")

```

# Improve pledge process

```{r,warning = FALSE, message = FALSE, echo=FALSE}

# How could your pledge progress be improved?


names(ENG)[11] <- "Improvement"

names(FRA)[11] <- "Improvement"

names(ESP)[11] <- "Improvement"

# Change French into English


replace_French_Improvement <- function(x,y){
  str_replace_all(FRA$Improvement, x, y)
}


FRA$Improvement <- replace_French_Improvement("Échanger avec d'autres contributeurs","Exchanging with fellow pledgemakers")

FRA$Improvement <- replace_French_Improvement("Bénéficier d’un appui technique","Receiving technical support")

FRA$Improvement <- replace_French_Improvement("Bénéficier d’un appui financier","Receiving financial support")


FRA$Improvement <- replace_French_Improvement("Volonté politique accrue","Increased political will")


FRA$Improvement <- replace_French_Improvement("Autre","Other")




# Change Spanish into English

replace_Spanish_Improvement <- function(x,y){
  str_replace_all(ESP$Improvement, x, y)
}



ESP$Improvement <- replace_Spanish_Improvement("Hablando con otras personas que han hecho compromisos de acción","Exchanging with fellow pledgemakers")

ESP$Improvement <- replace_Spanish_Improvement("Con más apoyo técnico","Receiving technical support")

ESP$Improvement <- replace_Spanish_Improvement("Con más apoyo económico","Receiving financial support")


ESP$Improvement <- replace_Spanish_Improvement("Con más voluntad política","Increased political will")


ESP$Improvement <- replace_Spanish_Improvement("Otra respuesta","Other")



# Convert to ind. dataframes and bind together



eng_improvement <- data.frame(ENG$Improvement) 
names(eng_improvement) <- "Improvement"

fra_improvement <- data.frame(FRA$Improvement) 
names(fra_improvement) <- "Improvement"

esp_improvement <- data.frame(ESP$Improvement)
names(esp_improvement) <- "Improvement"


improvement <- rbind(eng_improvement,fra_improvement,esp_improvement)



# Seperate w/ receiving

improvement <- improvement %>%
    mutate(Improvement = strsplit(as.character(Improvement), ", R")) %>% 
    unnest(Improvement)

improvement$Improvement <- ifelse(startsWith(improvement$Improvement, 'ec'), str_replace_all(improvement$Improvement,"eceiving","Receiving"),improvement$Improvement)

# Same for Increased

improvement <- improvement %>%  mutate(Improvement = strsplit(as.character(Improvement), ", I")) %>% 
    unnest(Improvement)


improvement$Improvement <- ifelse(startsWith(improvement$Improvement, 'ncreased'), str_replace_all(improvement$Improvement,"ncreased","Increased"),improvement$Improvement)



# Same for Other

improvement <- improvement %>%  mutate(Improvement = strsplit(as.character(Improvement), ", O")) %>%   unnest(Improvement)


improvement$Improvement <- ifelse(startsWith(improvement$Improvement, 'ther'), str_replace_all(improvement$Improvement,"ther","Other"),improvement$Improvement)



# Last, No 


improvement <- improvement %>%  mutate(Improvement = strsplit(as.character(Improvement), ", N")) %>%   unnest(Improvement)


improvement$Improvement <- ifelse(startsWith(improvement$Improvement, 'o '), str_replace_all(improvement$Improvement,"o ","No "),improvement$Improvement)


# Counting 


improvement <- improvement %>%
  count(Improvement) 

# Plot


improvement_plot <- plot_ly(improvement, labels = ~Improvement, values = ~n, type = 'pie',
                              marker = list(colors = colors,
                      line = list(color = '#FFFFFF', width = 1)))


improvement_plot <- improvement_plot %>% layout(title = 'How could your pledge progress be improved? <br> (Multiple Choice)',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))



improvement_plot

```

<h3>Improve pledge process - Other</h3>

```{r,warning = FALSE, message = FALSE, echo=FALSE}

improvement_other_df1 <- other_table(12,30)

DT::datatable(improvement_other_df1,caption= "Improve pledge process - Other")


```


## Receiving financial support

```{r,warning = FALSE, message = FALSE , echo=FALSE}


fin_support_df1 <- other_table(13,31)

DT::datatable(fin_support_df1,caption= "In which areas would you need financial support?")


```


## Receiving technical support

```{r,warning = FALSE, message = FALSE , echo=FALSE}


technical_support_df1 <- other_table(14,32)

DT::datatable(technical_support_df1,caption= "In which areas would you need technical support?")


```




# Share progress / inspire others


```{r,warning = FALSE, message = FALSE , echo=FALSE}

# How could we help you to share progress and inspire others?



names(ENG)[15] <- "share_progress"
names(FRA)[15] <- "share_progress"
names(ESP)[15] <- "share_progress"





# Change French into English


replace_French_share_progress <- function(x,y){
  str_replace_all(FRA$share_progress, x, y)
}




FRA$share_progress <- replace_French_share_progress("Proposer un jumelage avec d'autres contributeurs","Offer matchmaking with other plegdemakers")

FRA$share_progress <- replace_French_share_progress("Aide à la rédaction d'une histoire/d'un article de blog","Support in writing a story/blog post")

FRA$share_progress<- replace_French_share_progress("Création d'un compte sur les réseaux sociaux","Setting up a social media account")


#FRA$share_progress<- replace_French_share_progress("","No help required")






# Change Spanish into English

replace_Spanish_share_progress <- function(x,y){
  str_replace_all(ESP$share_progress, x, y)
}



ESP$share_progress <- replace_Spanish_share_progress("Proponiendo alianzas con otras personas que han hecho compromisos de acción","Offer matchmaking with other plegdemakers")

ESP$share_progress <- replace_Spanish_share_progress("Con apoyo para escribir una historia o una entrada de blog","Support in writing a story/blog post")

#ESP$share_progress<- replace_French_share_progress("","Setting up a social media account")


#ESP$share_progress<- replace_French_share_progress("","No help required")


ESP$share_progress <- replace_Spanish_share_progress("Otra respuesta","Other")





# Convert to ind. dataframes and bind together



eng_share_progress <- data.frame(ENG$share_progress) 
names(eng_share_progress) <- "share_progress"

fra_share_progress <- data.frame(FRA$share_progress) 
names(fra_share_progress) <- "share_progress"

esp_share_progress <- data.frame(ESP$share_progress)
names(esp_share_progress) <- "share_progress"


share_progress <- rbind(eng_share_progress,fra_share_progress,esp_share_progress)





share_progress <- share_progress %>%
    mutate(share_progress = strsplit(as.character(share_progress), ", S")) %>% 
    unnest(share_progress)



share_progress$share_progress <- ifelse(startsWith(share_progress$share_progress, 'upport'), str_replace_all(share_progress$share_progress,"upport","Support"),share_progress$share_progress)

share_progress$share_progress <- ifelse(startsWith(share_progress$share_progress, 'etting'), str_replace_all(share_progress$share_progress,"etting","Setting"),share_progress$share_progress)



# Counting 


share_progress <- share_progress %>%
  count(share_progress) 



share_progress_plot <- plot_ly(share_progress, labels = ~share_progress, values = ~n, type = 'pie',
                              marker = list(colors = colors,
                      line = list(color = '#FFFFFF', width = 1)))


share_progress_plot <- share_progress_plot %>% layout(title = 'How could we help you to share progress <br> and inspire others? (Multiple Choice)',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))


share_progress_plot


```

<h3> Share progress / inspire others </h3> 

```{r,warning = FALSE, message = FALSE , echo=FALSE}


share_progress_other_df1 <- other_table(16,31)

DT::datatable(share_progress_other_df1,caption= "Share Progress/ Inspire others - Other")


```

# Making another pledge next year

```{r,warning = FALSE, message = FALSE , echo=FALSE}


# Would you consider making another Action Pledge next year?



names(ENG)[17] <- "Action_Pledge"

names(FRA)[17] <- "Action_Pledge"

names(ESP)[17] <- "Action_Pledge"




# Change French into English




FRA$Action_Pledge <- str_replace_all(FRA$Action_Pledge,"Oui","Yes")

FRA$Action_Pledge <- str_replace_all(FRA$Action_Pledge,"Peut-être","Maybe")

#FRA$Action_Pledge <- str_replace_all(FRA$Action_Pledge,"Non","No")



# Change Spanish into English


ESP$Action_Pledge <- str_replace_all(ESP$Action_Pledge,"Sí","Yes")

#ESP$Action_Pledge <- str_replace_all(ESP$Action_Pledge,"Peut-être","Maybe")

#ESP$Action_Pledge <- str_replace_all(ESP$Action_Pledge,"Non","No")





# Convert to ind. dataframes and bind together



eng_Action_Pledge <- data.frame(ENG$Action_Pledge) 
names(eng_Action_Pledge) <- "Action_Pledge"

fra_Action_Pledge <- data.frame(FRA$Action_Pledge) 
names(fra_Action_Pledge) <- "Action_Pledge"

esp_Action_Pledge <- data.frame(ESP$Action_Pledge)
names(esp_Action_Pledge) <- "Action_Pledge"


Action_Pledge <- rbind(eng_Action_Pledge,fra_Action_Pledge,esp_Action_Pledge)





Action_Pledge <- Action_Pledge %>%
  count(Action_Pledge) 



Action_Pledge_plot <- plot_ly(Action_Pledge, labels = ~Action_Pledge, values = ~n, type = 'pie',
                              marker = list(colors = colors,
                      line = list(color = '#FFFFFF', width = 1)))


Action_Pledge_plot <- Action_Pledge_plot %>% layout(title = ' Would you consider making another Action Pledge next year?',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))


Action_Pledge_plot

```
  

<h3> Another Pledge - Maybe </h3>

```{r,warning = FALSE, message = FALSE , echo=FALSE}


share_progress_other_df1 <- other_table(18,34)

DT::datatable(share_progress_other_df1,caption= "Making another Action Pledge - Maybe")


```



# Trello Board


Have you used any of the materials available on the End Child Labour 2021 Trello board [https://trello.com/b/U5dZZCNw/end-child-labour-2021](https://trello.com/b/U5dZZCNw/end-child-labour-2021) to create or share content?


```{r,warning = FALSE, message = FALSE , echo=FALSE}




names(ENG)[19] <- "Trello_Board"

names(FRA)[19] <- "Trello_Board"

names(ESP)[19] <- "Trello_Board"




# Change French into English




FRA$Trello_Board <- str_replace_all(FRA$Trello_Board,"Oui","Yes")


FRA$Trello_Board <- str_replace_all(FRA$Trello_Board,"Non","No")



# Change Spanish into English


ESP$Trello_Board <- str_replace_all(ESP$Trello_Board,"Sí","Yes")

#ESP$Action_Pledge <- str_replace_all(ESP$Action_Pledge,"Peut-être","Maybe")

#ESP$Action_Pledge <- str_replace_all(ESP$Action_Pledge,"Non","No")


# Convert to ind. dataframes and bind together



eng_Trello_Board <- data.frame(ENG$Trello_Board) 
names(eng_Trello_Board) <- "Trello_Board"

fra_Trello_Board  <- data.frame(FRA$Trello_Board) 
names(fra_Trello_Board) <- "Trello_Board"

esp_Trello_Board <- data.frame(ESP$Trello_Board)
names(esp_Trello_Board) <- "Trello_Board"


Trello_Board <- rbind(eng_Trello_Board,fra_Trello_Board,esp_Trello_Board)





Trello_Board <- Trello_Board %>%
  count(Trello_Board) 

# colors Trello
colors_Trello <- c('#CA0148', '#146C77')


Trello_Board_plot <- plot_ly(Trello_Board, labels = ~Trello_Board, values = ~n, type = 'pie',
                              marker = list(colors = colors_Trello,
                      line = list(color = '#FFFFFF', width = 1)))


Trello_Board_plot <- Trello_Board_plot %>% layout(title = 'Have you used any of the materials available <br>on the End Child Labour 2021 Trello board?<br>',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))


Trello_Board_plot

```



# Using #EndChildLabour2021


```{r,warning = FALSE, message = FALSE , echo=FALSE}
names(ENG)[20] <- "hashtag"
names(FRA)[20] <- "hashtag"
names(ESP)[20] <- "hashtag"




# Change French into English


replace_French_hashtag <- function(x,y){
  str_replace_all(FRA$hashtag, x, y)
}



#FRA$hashtag <- str_replace_all(FRA$hashtag,'Pas souvent (au moins une fois depuis juin 2021)','Not often (at least once since June 2021)')

# The upper does not work, hence working with ifelse
FRA$hashtag <- ifelse(startsWith(FRA$hashtag, 'Pas souvent'),"Not often (at least once since June 2021)",FRA$hashtag)
                    

#FRA$hashtag <- replace_French_hashtag("Parfois (au moins trois fois depuis juin 2021)","Sometimes (at least three times since June 2021)")

FRA$hashtag <- ifelse(startsWith(FRA$hashtag, 'Parfois'),"Sometimes (at least three times since June 2021)",FRA$hashtag)



#FRA$hashtag<- replace_French_hashtag("Régulièrement (au moins une fois par mois)","Regularly (at least once a month)")

FRA$hashtag <- ifelse(startsWith(FRA$hashtag, 'Régulièrement'),"Regularly (at least once a month)",FRA$hashtag)

FRA$hashtag<- replace_French_hashtag("Jamais","Never")



# Spanish to English

replace_Spanish_hashtag <- function(x,y){
  str_replace_all(ESP$hashtag, x, y)
}




#ESP$hashtag <- replace_Spanish_hashtag("A veces (al menos tres veces desde junio de 2021)","Sometimes (at least three times since June 2021)")

ESP$hashtag <- ifelse(startsWith(ESP$hashtag, 'A veces'),"Sometimes (at least three times since June 2021)",ESP$hashtag)



#ESP$hashtag<- replace_Spanish_hashtag("A menudo (al menos una vez al mes)","Regularly (at least once a month)")


ESP$hashtag <- ifelse(startsWith(ESP$hashtag, 'A menudo'),"Regularly (at least once a month)",ESP$hashtag)

ESP$hashtag<- replace_Spanish_hashtag("Nunca","Never")



# Convert to ind. dataframes and bind together



eng_hashtag <- data.frame(ENG$hashtag) 
names(eng_hashtag) <- "hashtag"

fra_hashtag <- data.frame(FRA$hashtag) 
names(fra_hashtag) <- "hashtag"

esp_hashtag <- data.frame(ESP$hashtag)
names(esp_hashtag) <- "hashtag"


hashtag <- rbind(eng_hashtag,fra_hashtag,esp_hashtag)





hashtag <- hashtag %>%
  count(hashtag) 



hashtag_plot <- plot_ly(hashtag, labels = ~hashtag, values = ~n, type = 'pie',
                              marker = list(colors = colors,
                      line = list(color = '#FFFFFF', width = 1)))


hashtag_plot <- hashtag_plot %>% layout(title = 'How often did you post about your pledge <br> using the hashtag #EndChildLabour2021?',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))


hashtag_plot


```



# Receiving Information about International Year

```{r,warning = FALSE, message = FALSE , echo=FALSE}


# Where do you receive information about the 2021 International Year from?



names(ENG)[22] <- "Information"

names(FRA)[22] <- "Information"

names(ESP)[22] <- "Information"


# Change French into English


replace_French_Information <- function(x,y){
  str_replace_all(FRA$Information, x, y)
}




FRA$Information <- replace_French_Information("E-mails de liste de diffusion","Mailing list emails")


FRA$Information <- replace_French_Information("Site Internet","Website")

FRA$Information <- replace_French_Information("Autre","Other")

FRA$Information <- replace_French_Information("Je ne reçois pas d'informations","I did not receive information")




# Change Spanish into English



replace_Spanish_Information <- function(x,y){
  str_replace_all(ESP$Information, x, y)
}




ESP$Information <- replace_Spanish_Information("Lista de distribución de correo electrónico","Mailing list emails")

ESP$Information <- replace_Spanish_Information("Página web","Website")







# Convert to ind. dataframes and bind together



eng_Information <- data.frame(ENG$Information) 
names(eng_Information) <- "Information"

fra_Information <- data.frame(FRA$Information) 
names(fra_Information) <- "Information"

esp_Information <- data.frame(ESP$Information)
names(esp_Information) <- "Information"


information <- rbind(eng_Information,fra_Information,esp_Information)



# Split after comma



information <- information %>%
    mutate(Information = strsplit(as.character(Information), ", ")) %>% 
    unnest(Information)



##


information <- information %>%
  count(Information) 


colors2 <- c('#8D094A', '#CA0148', '#146C77', '#F6B940', '#052538','#A5A5A5','#FC9C08','#CA0148')



information$Information <- factor(information$Information, levels = unique(information$Information)[order(information$n, decreasing = TRUE)])



fig_information <- plot_ly(information, y = ~n, x = ~Information, color= ~Information, type = 'bar',
              marker = list(colors = colors2,
                   line = list(color = '#FFFFFF', width = 1)))


fig_information <- fig_information %>% layout(title = 'Where do you receive information <br> about the 2021 International Year from? (Multiple Choice)',showlegend = FALSE,margin = list(b = 160), xaxis = list(tickfont = list(size = 12)))

fig_information


```



<h3>Receiving information about International Year - Other</h3>

```{r,warning = FALSE, message = FALSE , echo=FALSE}


share_progress_other_df1 <- other_table(23,35)

DT::datatable(share_progress_other_df1,caption= "Receiving information - Other")


```

# Learning about Child Labour


```{r,warning = FALSE, message = FALSE , echo=FALSE}

#9) Do you feel that you learnt more about child labour this year?


names(ENG)[24] <- "learn_CL"
names(FRA)[24] <- "learn_CL"
names(ESP)[24] <- "learn_CL"





# Change French into English


replace_French_learn_CL <- function(x,y){
  str_replace_all(FRA$learn_CL, x, y)
}




FRA$learn_CL <- replace_French_learn_CL("J'ai appris plus sur la complexité du travail des enfants","I learnt more about the complexity of child labour")

FRA$learn_CL <- replace_French_learn_CL("J'ai appris plus sur les causes profondes du travail des enfants","I learnt more about the root causes of child labour")

FRA$learn_CL<- replace_French_learn_CL("J'ai appris plus sur les différents acteurs œuvrant contre le travail des enfants","I learnt more about the different actors working against child labour")


FRA$learn_CL<- replace_French_learn_CL("J'ai appris plus sur les solutions potentielles contre le travail des enfants","I learnt more about potential solutions against child labour")

FRA$learn_CL<- replace_French_learn_CL("Non, je n'ai pas l'impression d'avoir appris grand-chose de nouveau sur le travail des enfants cette année","No, I don’t feel I learnt much new about child labour this year")

#FRA$learn_CL<- replace_French_learn_CL("","Other")



# Change Spanish into English

replace_Spanish_learn_CL <- function(x,y){
  str_replace_all(ESP$learn_CL, x, y)
}



ESP$learn_CL <- replace_Spanish_learn_CL("He aprendido más cosas sobre la complejidad del trabajo infantil","I learnt more about the complexity of child labour")

ESP$learn_CL <- replace_Spanish_learn_CL("He aprendido más cosas sobre las causas fundamentales del trabajo infantil","I learnt more about the root causes of child labour")

ESP$learn_CL<- replace_Spanish_learn_CL("He aprendido más cosas sobre los distintos actores trabajando contra el trabajo infantil","I learnt more about the different actors working against child labour")


ESP$learn_CL<- replace_Spanish_learn_CL("He aprendido más cosas sobre las posibles soluciones para acabar con el trabajo infantil","I learnt more about potential solutions against child labour")

ESP$learn_CL<- replace_Spanish_learn_CL("Non, je n'ai pas l'impression d'avoir appris grand-chose de nouveau sur le travail des enfants cette année","No, I don’t feel I learnt much new about child labour this year")

#ESP$learn_CL<- replace_Spanish_learn_CL("","Other")




# Convert to ind. dataframes and bind together



eng_learn_CL <- data.frame(ENG$learn_CL) 
names(eng_learn_CL) <- "learn_CL"

fra_learn_CL <- data.frame(FRA$learn_CL) 
names(fra_learn_CL) <- "learn_CL"

esp_learn_CL <- data.frame(ESP$learn_CL)
names(esp_learn_CL) <- "learn_CL"


learn_CL <- rbind(eng_learn_CL,fra_learn_CL,esp_learn_CL)



learn_CL <- learn_CL %>%
    mutate(learn_CL = strsplit(as.character(learn_CL), ", I")) %>% 
    unnest(learn_CL)

learn_CL<-learn_CL[!(learn_CL$learn_CL=="No"),]


learn_CL$learn_CL <- ifelse(startsWith(learn_CL$learn_CL, ' learnt'), str_replace_all(learn_CL$learn_CL," learnt","I learnt"),learn_CL$learn_CL)

learn_CL$learn_CL <- ifelse(startsWith(learn_CL$learn_CL, ' don'), str_replace_all(learn_CL$learn_CL," don","No, I don"),learn_CL$learn_CL)




# Counting 


learn_CL <- learn_CL %>%
  count(learn_CL) 



learn_CL_plot <- plot_ly(learn_CL, labels = ~learn_CL, values = ~n, type = 'pie',
                              marker = list(colors = colors,
                      line = list(color = '#FFFFFF', width = 1)))


learn_CL_plot <- learn_CL_plot %>% layout(title = 'Do you feel that you learnt more about <br> child labour this year? (Multiple Choice)',
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))


learn_CL_plot


```



<h3> Learning about Child Labour - Other </h3>

```{r,warning = FALSE, message = FALSE , echo=FALSE}


share_progress_other_df1 <- other_table(25,36)

DT::datatable(share_progress_other_df1,caption= "Learning about Child Labour - Other")


```

